Light inextensible strings (threads) under tension in the Schwarzschild geometry: a new interpretation for ``straight line'' in general relativity

### 2020-10-21 string_physics_teacher_revision.tex
capitalization

\begin{enumerate}
\item null geodesics: paths for which $ds^2=0$ at all points.  Light
  travels on null geodesics and is arguably the ``straightest'' of
  straight lines.
\item timelike geodesics: paths for which $ds^2>0$ everywhere, and for
  which $\int\sqrt{ds^2}$ is a minimum.  These are the paths that
  objects in freefall follow.
\item taut string: paths for which $dt=0$, thereby considering the
  configuration of a string.  If the proper length
  $\int\sqrt{dr^2+r^2d\theta^2}$ is a minimum, the string is taut in
  the sense that its inchworm-measured length is a minimum.
\end{enumerate}

>>>>

\begin{enumerate}
\item Null geodesics: paths for which $ds^2=0$ at all points.  Light
  travels on null geodesics and is arguably the ``straightest'' of
  straight lines.
\item Timelike geodesics: paths for which $ds^2>0$ everywhere, and for
  which $\int\sqrt{ds^2}$ is a minimum.  These are the paths that
  objects in freefall follow.
\item Taut string: paths for which $dt=0$, thereby considering the
  configuration of a string.  If the proper length
  $\int\sqrt{dr^2+r^2d\theta^2}$ is a minimum, the string is taut in
  the sense that its inchworm-measured length is a minimum.
\end{enumerate}
